### 2018-01-28 latex/MOSIM2018/article.tex
Corrected some errors in tables mentioned by Nicolas
small other changes that were missing from MOSIM article. Re-executed multi-multi table.

  It should be noted that previous formulations only consider an aggregate demand in flight hours for all aircraft.
  The aircraft are assumed to be homogeneous and interchangeable.
  The use of aggregate demand makes it impossible to optimize the task assignments for aircraft.
   % The concept of mission is not introduced as part of these formulations, only a demand of flight hours is given for all aircraft in total. The aircraft themselves have been assumed as homogeneous and interchangeable. Due to this aggregation of demand, there are no minimal time assignments for aircraft to missions. Missions are important in order to guarantee that aircraft have the required capabilities needed for the missions they are assigned to.

@@

    All maintenance operations last exactly 6 periods. Each maintenance provides with 1000 hours of usage time to the resource. After it, a resource can be without maintenance for a maximum of 60 consecutive periods. The nominative capacity for maintenance is 18 resources at any given time.

@@

    Table \ref{tab:results2} shows the progress of the integer solution for each instance. For more detail on this progress, figure \ref{fig:progress} shows an example of progress for instance with id=I\_7. It can be seen that initial solutions are quite big in comparison with the optimal due to the use of heuristics being run at the beginning of the solving process. In fact, for two rather small instances the solver was able to find an optimal solution before starting to branch.

>>>>

  It should be noted that previous formulations only consider an aggregate demand in flight hours for all aircraft.
  The aircraft are assumed to be homogeneous and interchangeable.
  The use of aggregate demand makes it impossible to take into account the task requirements for aircraft.
   % The concept of mission is not introduced as part of these formulations, only a demand of flight hours is given for all aircraft in total. The aircraft themselves have been assumed as homogeneous and interchangeable. Due to this aggregation of demand, there are no minimal time assignments for aircraft to missions. Missions are important in order to guarantee that aircraft have the required capabilities needed for the missions they are assigned to.

@@

    All maintenance operations last exactly 6 periods. Each maintenance sets the remaining usage time of a resource to 1000 hours. After it, a resource can be without maintenance for a maximum of 60 consecutive periods. The nominative capacity for maintenance is 18 resources at any given time.

@@

    Table \ref{tab:results2} shows the progress of the integer solution for each instance. For more detail on this progress, figure \ref{fig:progress} shows an example of progress for instance with id=I\_7. It can be seen that initial solutions are quite far from the optimal one due to the use of heuristics at the beginning of the solving process. In fact, for two rather small instances the solver was able to find an optimal solution before starting to branch.
